---
title: "ASPengdaDataset"
author: "Kwame Forbes"
date: "10/3/2022"
output: html_document
---
load Dependencies
```{r}
install.packages("tidyr")
library(tidyr)
install.packages("plyr")
library("plyr")
install.packages("devtools")
library(devtools)
devtools::install_github("kassambara/ggpubr")
install.packages("ggpubr")
library(ggpubr)
install.packages('scrime')
library("scrime")
library(pheatmap)
```



Variables
```{r}
IncLevelDifference.variable = 0.1
FDR.variable = 0.05
coverage = 50
PSIDiff = 0.1
```



Function to get PSI Difference
```{r}
f <- function(x, ...) {
  abs(max(x) -min(x))
}
mx <- function(x, ..) {
  round(mean(x),2)
}
```



WT vs T200M RI JC 
```{r}
WTvT200M_ri_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvT200M/BAM/RI.MATS.JC.txt",header = T)
WTvT200M_ri_jc <- as.data.frame(WTvT200M_ri_jc)

AS = as.data.frame(rep("RI",dim(WTvT200M_ri_jc)[1]))
names(AS)[names(AS) == 'rep("RI", dim(WTvT200M_ri_jc)[1])'] <- "events"
WTvT200M_ri_jc = cbind(WTvT200M_ri_jc,AS)
Comparison = as.data.frame(rep("WTvT200M",dim(WTvT200M_ri_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvT200M", dim(WTvT200M_ri_jc)[1])'] <- "Comparison"
WTvT200M_ri_jc = cbind(WTvT200M_ri_jc,Comparison)

WTvT200M_ri_jc = unite(WTvT200M_ri_jc,"Position",c(4:11),sep = ":",remove = T)
WTvT200M_ri_jc$EVENT <- paste(WTvT200M_ri_jc$geneSymbol,WTvT200M_ri_jc$Position,sep = "_")
rownames(WTvT200M_ri_jc) <- WTvT200M_ri_jc$EVENT
WTvT200M_ri_jc <- subset(WTvT200M_ri_jc, select = -c(1:5))

WTvT200M_ri_jc <- separate(WTvT200M_ri_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_ri_jc <- separate(WTvT200M_ri_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_ri_jc <- separate(WTvT200M_ri_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_T200M1","IJC_SAMPLE_T200M2","IJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_ri_jc <- separate(WTvT200M_ri_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_T200M1","SJC_SAMPLE_T200M2","SJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_ri_jc[1:12] <- as.numeric(unlist(WTvT200M_ri_jc[1:12]))

WTvT200M_ri_jc <- separate(WTvT200M_ri_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvT200M_ri_jc <- separate(WTvT200M_ri_jc, col = IncLevel2, into = c("IncLevel_T200M1","IncLevel_T200M2","IncLevel_T200M3"),sep = ",",remove = T)
WTvT200M_ri_jc[17:22] <- as.numeric(unlist(WTvT200M_ri_jc[17:22]))
WTvT200M_ri_jc <- na.omit(WTvT200M_ri_jc)
WTvT200M_ri_jc$PSIDiff <- (apply(WTvT200M_ri_jc[17:22], MARGIN =  1, f,))
WTvT200M_ri_jc$Coverage <- (apply(WTvT200M_ri_jc[c(1:3,7:9)], MARGIN = 1,mx,))
```
Filtering WT vs T200M RI JC average reads, abs(IncLevelDifference), and FDR 
```{r}
WTvT200M_ri_jc = subset(WTvT200M_ri_jc,Coverage >=coverage)
WTvT200M_ri_jc <- subset(WTvT200M_ri_jc, abs(IncLevelDifference) >= IncLevelDifference.variable & FDR <= FDR.variable)
```

Plots
```{r}
p <- ggplot(data = WTvT200M_ri_jc,mapping= 
              aes(IncLevelDifference,-log(FDR)))+ theme_classic() + geom_point(color = ifelse(WTvT200M_ri_jc$IncLevelDifference >= 0.1 ,"blue","red")) + 
  theme_classic()+ ggtitle("WT vs. T200M RI PSI") +xlab("PSI Change") + ylab("-log10(FDR)")
pp <- p+ theme(plot.title = element_text(color="red", size=14, face="bold.italic"),
         axis.title.x = element_text(color="blue", size=14, face="bold"),
         axis.title.y = element_text(color="#993333", size=14, face="bold"))

s <- ggplot(WTvT200M_ri_jc, aes(x="WTvT200M", y=IncLevelDifference)) + 
   theme_classic()+ ggtitle("RI PSI of WTvT200M") + ylab("IncLevelDifference") + geom_violin()

s2 <- s + theme(plot.title = element_text(color="red", size=14, face="bold.italic"),
         axis.title.x = element_text(color="blue", size=14, face="bold"),
         axis.title.y = element_text(color="#993333", size=14, face="bold"))
 
s2 <- s2 + geom_boxplot(width=0.2)

sg <- ggarrange(pp,s2, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
sg
```


WT vs EV RI JC
```{r}
WTvEV_ri_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvEV/BAM/RI.MATS.JC.txt",header = T)
WTvEV_ri_jc <- as.data.frame(WTvEV_ri_jc)

AS = as.data.frame(rep("RI",dim(WTvEV_ri_jc)[1]))
names(AS)[names(AS) == 'rep("RI", dim(WTvEV_ri_jc)[1])'] <- "events"
WTvEV_ri_jc = cbind(WTvEV_ri_jc,AS)
Comparison = as.data.frame(rep("WTvEV",dim(WTvEV_ri_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvEV", dim(WTvEV_ri_jc)[1])'] <- "Comparison"
WTvEV_ri_jc = cbind(WTvEV_ri_jc,Comparison)

WTvEV_ri_jc = unite(WTvEV_ri_jc,"Position",c(4:11),sep = ":",remove = T)
WTvEV_ri_jc$EVENT <- paste(WTvEV_ri_jc$geneSymbol,WTvEV_ri_jc$Position,sep = "_")
rownames(WTvEV_ri_jc) <- WTvEV_ri_jc$EVENT
WTvEV_ri_jc <- subset(WTvEV_ri_jc, select = -c(1:5))

WTvEV_ri_jc <- separate(WTvEV_ri_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_ri_jc <- separate(WTvEV_ri_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_ri_jc <- separate(WTvEV_ri_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_EV1","IJC_SAMPLE_EV2","IJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_ri_jc <- separate(WTvEV_ri_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_EV1","SJC_SAMPLE_EV2","SJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_ri_jc[1:12] <- as.numeric(unlist(WTvEV_ri_jc[1:12]))

WTvEV_ri_jc <- separate(WTvEV_ri_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvEV_ri_jc <- separate(WTvEV_ri_jc, col = IncLevel2, into = c("IncLevel_EV1","IncLevel_EV2","IncLevel_EV3"),sep = ",",remove = T)
WTvEV_ri_jc[17:22] <- as.numeric(unlist(WTvEV_ri_jc[17:22]))
WTvEV_ri_jc <- na.omit(WTvEV_ri_jc)
WTvEV_ri_jc$PSIDiff <- (apply(WTvEV_ri_jc[17:22], MARGIN =  1, f,))
WTvEV_ri_jc$Coverage <- (apply(WTvEV_ri_jc[c(1:3,7:9)], MARGIN = 1,mx,))
```




Filtering WT vs EV RI JC by average reads, abs(IncLevelDifference), and FDR 
```{r}
WTvEV_ri_jc = subset(WTvEV_ri_jc,Coverage >=coverage)
WTvEV_ri_jc <- subset(WTvEV_ri_jc, abs(IncLevelDifference) >= IncLevelDifference.variable & FDR <= FDR.variable)
```



Combining RI (Only Events that have all three levels are included) this further filters the list
```{r}
RI <- merge(WTvT200M_ri_jc,WTvEV_ri_jc,by="EVENT")
colnames(RI)<-gsub(".x","",colnames(RI))
RI <- subset(RI, select = c(1:13,35:40,18:23,48:50,25))
```



WT vs T200M SE JC
```{r}
WTvT200M_se_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvT200M/BAM/SE.MATS.JC.txt",header = T)
WTvT200M_se_jc <- as.data.frame(WTvT200M_se_jc)

AS = as.data.frame(rep("SE",dim(WTvT200M_se_jc)[1]))
names(AS)[names(AS) == 'rep("SE", dim(WTvT200M_se_jc)[1])'] <- "events"
WTvT200M_se_jc = cbind(WTvT200M_se_jc,AS)
Comparison = as.data.frame(rep("WTvT200M",dim(WTvT200M_se_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvT200M", dim(WTvT200M_se_jc)[1])'] <- "Comparison"
WTvT200M_se_jc = cbind(WTvT200M_se_jc,Comparison)

WTvT200M_se_jc = unite(WTvT200M_se_jc,"Position",c(4:11),sep = ":",remove = T)
WTvT200M_se_jc$EVENT <- paste(WTvT200M_se_jc$geneSymbol,WTvT200M_se_jc$Position,sep = "_")
rownames(WTvT200M_se_jc) <- WTvT200M_se_jc$EVENT
WTvT200M_se_jc <- subset(WTvT200M_se_jc, select = -c(1:5))

WTvT200M_se_jc <- separate(WTvT200M_se_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_se_jc <- separate(WTvT200M_se_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_se_jc <- separate(WTvT200M_se_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_T200M1","IJC_SAMPLE_T200M2","IJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_se_jc <- separate(WTvT200M_se_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_T200M1","SJC_SAMPLE_T200M2","SJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_se_jc[1:12] <- as.numeric(unlist(WTvT200M_se_jc[1:12]))

WTvT200M_se_jc <- separate(WTvT200M_se_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvT200M_se_jc <- separate(WTvT200M_se_jc, col = IncLevel2, into = c("IncLevel_T200M1","IncLevel_T200M2","IncLevel_T200M3"),sep = ",",remove = T)
WTvT200M_se_jc[17:22] <- as.numeric(unlist(WTvT200M_se_jc[17:22]))
WTvT200M_se_jc <- na.omit(WTvT200M_se_jc)
WTvT200M_se_jc$PSIDiff <- (apply(WTvT200M_se_jc[17:22], MARGIN =  1, f,))
WTvT200M_se_jc$Coverage <- (apply(WTvT200M_se_jc[c(1:3,7:9)], MARGIN = 1,mx,))
```



Filtering WT vs T200M SE JC by average reads, abs(IncLevelDifference), and FDR 
```{r}
WTvT200M_se_jc = subset(WTvT200M_se_jc,Coverage >=coverage)
WTvT200M_se_jc <- subset(WTvT200M_se_jc, abs(IncLevelDifference) >= IncLevelDifference.variable & FDR <= FDR.variable)
```



WT vs EV SE JC
```{r}
WTvEV_se_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvEV/BAM/SE.MATS.JC.txt",header = T)
WTvEV_se_jc <- as.data.frame(WTvEV_se_jc)

AS = as.data.frame(rep("SE",dim(WTvEV_se_jc)[1]))
names(AS)[names(AS) == 'rep("SE", dim(WTvEV_se_jc)[1])'] <- "events"
WTvEV_se_jc = cbind(WTvEV_se_jc,AS)
Comparison = as.data.frame(rep("WTvEV",dim(WTvEV_se_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvEV", dim(WTvEV_se_jc)[1])'] <- "Comparison"
WTvEV_se_jc = cbind(WTvEV_se_jc,Comparison)

WTvEV_se_jc = unite(WTvEV_se_jc,"Position",c(4:11),sep = ":",remove = T)
WTvEV_se_jc$EVENT <- paste(WTvEV_se_jc$geneSymbol,WTvEV_se_jc$Position,sep = "_")
rownames(WTvEV_se_jc) <- WTvEV_se_jc$EVENT
WTvEV_se_jc <- subset(WTvEV_se_jc, select = -c(1:5))

WTvEV_se_jc <- separate(WTvEV_se_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_se_jc <- separate(WTvEV_se_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_se_jc <- separate(WTvEV_se_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_EV1","IJC_SAMPLE_EV2","IJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_se_jc <- separate(WTvEV_se_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_EV1","SJC_SAMPLE_EV2","SJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_se_jc[1:12] <- as.numeric(unlist(WTvEV_se_jc[1:12]))

WTvEV_se_jc <- separate(WTvEV_se_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvEV_se_jc <- separate(WTvEV_se_jc, col = IncLevel2, into = c("IncLevel_EV1","IncLevel_EV2","IncLevel_EV3"),sep = ",",remove = T)
WTvEV_se_jc[17:22] <- as.numeric(unlist(WTvEV_se_jc[17:22]))
WTvEV_se_jc <- na.omit(WTvEV_se_jc)
WTvEV_se_jc$PSIDiff <- (apply(WTvEV_se_jc[17:22], MARGIN =  1, f,))
WTvEV_se_jc$Coverage <- (apply(WTvEV_se_jc[c(1:3,7:9)], MARGIN = 1,mx,))
```



Filtering WT vs EV SE JC by average reads, abs(IncLevelDifference), and FDR 
```{r}
WTvEV_se_jc = subset(WTvEV_se_jc,Coverage >=coverage)
WTvEV_se_jc <- subset(WTvEV_se_jc, abs(IncLevelDifference) >= IncLevelDifference.variable & FDR <= FDR.variable)
```



Combining SE (Only Events that have all three levels are included) this further filters the list
```{r}
SE <- merge(WTvT200M_se_jc,WTvEV_se_jc,by="EVENT",)
colnames(SE)<-gsub(".x","",colnames(SE))
SE <- subset(SE, select = c(1:13,35:40,18:23,48:50,25))
```



WT vs T200M A3SS JC
```{r}
WTvT200M_a3ss_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvT200M/BAM/A3SS.MATS.JC.txt",header = T)
WTvT200M_a3ss_jc <- as.data.frame(WTvT200M_a3ss_jc)

AS = as.data.frame(rep("A3SS",dim(WTvT200M_a3ss_jc)[1]))
names(AS)[names(AS) == 'rep("A3SS", dim(WTvT200M_a3ss_jc)[1])'] <- "events"
WTvT200M_a3ss_jc = cbind(WTvT200M_a3ss_jc,AS)
Comparison = as.data.frame(rep("WTvT200M",dim(WTvT200M_a3ss_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvT200M", dim(WTvT200M_a3ss_jc)[1])'] <- "Comparison"
WTvT200M_a3ss_jc = cbind(WTvT200M_a3ss_jc,Comparison)

WTvT200M_a3ss_jc = unite(WTvT200M_a3ss_jc,"Position",c(4:11),sep = ":",remove = T)
WTvT200M_a3ss_jc$EVENT <- paste(WTvT200M_a3ss_jc$geneSymbol,WTvT200M_a3ss_jc$Position,sep = "_")
rownames(WTvT200M_a3ss_jc) <- WTvT200M_a3ss_jc$EVENT
WTvT200M_a3ss_jc <- subset(WTvT200M_a3ss_jc, select = -c(1:5))

WTvT200M_a3ss_jc <- separate(WTvT200M_a3ss_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_a3ss_jc <- separate(WTvT200M_a3ss_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_a3ss_jc <- separate(WTvT200M_a3ss_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_T200M1","IJC_SAMPLE_T200M2","IJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_a3ss_jc <- separate(WTvT200M_a3ss_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_T200M1","SJC_SAMPLE_T200M2","SJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_a3ss_jc[1:12] <- as.numeric(unlist(WTvT200M_a3ss_jc[1:12]))

WTvT200M_a3ss_jc <- separate(WTvT200M_a3ss_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvT200M_a3ss_jc <- separate(WTvT200M_a3ss_jc, col = IncLevel2, into = c("IncLevel_T200M1","IncLevel_T200M2","IncLevel_T200M3"),sep = ",",remove = T)
WTvT200M_a3ss_jc[17:22] <- as.numeric(unlist(WTvT200M_a3ss_jc[17:22]))
WTvT200M_a3ss_jc <- na.omit(WTvT200M_a3ss_jc)
WTvT200M_a3ss_jc$PSIDiff <- (apply(WTvT200M_a3ss_jc[17:22], MARGIN =  1, f,))
WTvT200M_a3ss_jc$Coverage <- (apply(WTvT200M_a3ss_jc[c(1:3,7:9)], MARGIN = 1,mx,))
```



Filtering WT vs T200M A3SS JC by average reads, abs(IncLevelDifference), and FDR 
```{r}
WTvT200M_a3ss_jc = subset(WTvT200M_a3ss_jc,Coverage >=coverage)
WTvT200M_a3ss_jc <- subset(WTvT200M_a3ss_jc, abs(IncLevelDifference) >= IncLevelDifference.variable & FDR <= FDR.variable)
```



WT vs EV A3SS JC
```{r}
WTvEV_a3ss_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvEV/BAM/A3SS.MATS.JC.txt",header = T)
WTvEV_a3ss_jc <- as.data.frame(WTvEV_a3ss_jc)

AS = as.data.frame(rep("A3SS",dim(WTvEV_a3ss_jc)[1]))
names(AS)[names(AS) == 'rep("A3SS", dim(WTvEV_a3ss_jc)[1])'] <- "events"
WTvEV_a3ss_jc = cbind(WTvEV_a3ss_jc,AS)
Comparison = as.data.frame(rep("WTvEV",dim(WTvEV_a3ss_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvEV", dim(WTvEV_a3ss_jc)[1])'] <- "Comparison"
WTvEV_a3ss_jc = cbind(WTvEV_a3ss_jc,Comparison)

WTvEV_a3ss_jc = unite(WTvEV_a3ss_jc,"Position",c(4:11),sep = ":",remove = T)
WTvEV_a3ss_jc$EVENT <- paste(WTvEV_a3ss_jc$geneSymbol,WTvEV_a3ss_jc$Position,sep = "_")
rownames(WTvEV_a3ss_jc) <- WTvEV_a3ss_jc$EVENT
WTvEV_a3ss_jc <- subset(WTvEV_a3ss_jc, select = -c(1:5))

WTvEV_a3ss_jc <- separate(WTvEV_a3ss_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_a3ss_jc <- separate(WTvEV_a3ss_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_a3ss_jc <- separate(WTvEV_a3ss_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_EV1","IJC_SAMPLE_EV2","IJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_a3ss_jc <- separate(WTvEV_a3ss_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_EV1","SJC_SAMPLE_EV2","SJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_a3ss_jc[1:12] <- as.numeric(unlist(WTvEV_a3ss_jc[1:12]))

WTvEV_a3ss_jc <- separate(WTvEV_a3ss_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvEV_a3ss_jc <- separate(WTvEV_a3ss_jc, col = IncLevel2, into = c("IncLevel_EV1","IncLevel_EV2","IncLevel_EV3"),sep = ",",remove = T)
WTvEV_a3ss_jc[17:22] <- as.numeric(unlist(WTvEV_a3ss_jc[17:22]))
WTvEV_a3ss_jc <- na.omit(WTvEV_a3ss_jc)
WTvEV_a3ss_jc$PSIDiff <- (apply(WTvEV_a3ss_jc[17:22], MARGIN =  1, f,))
WTvEV_a3ss_jc$Coverage <- (apply(WTvEV_a3ss_jc[c(1:3,7:9)], MARGIN = 1,mx,))
```



Filtering WT vs EV A3SS JC by average reads, abs(IncLevelDifference), and FDR 
```{r}
WTvEV_a3ss_jc = subset(WTvEV_a3ss_jc,Coverage >=coverage)
WTvEV_a3ss_jc <- subset(WTvEV_a3ss_jc, abs(IncLevelDifference) >= IncLevelDifference.variable & FDR <= FDR.variable)
```



Combining A3SS (Only Events that have all three levels are included) this further filters the list
```{r}
A3SS <- merge(WTvT200M_a3ss_jc,WTvEV_a3ss_jc,by="EVENT")
colnames(A3SS)<-gsub(".x","",colnames(A3SS))
A3SS <- subset(A3SS, select = c(1:13,35:40,18:23,48:50,25))
```



WT vs T200M A5SS JC
```{r}
WTvT200M_a5ss_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvT200M/BAM/A5SS.MATS.JC.txt",header = T)
WTvT200M_a5ss_jc <- as.data.frame(WTvT200M_a5ss_jc)

AS = as.data.frame(rep("A5SS",dim(WTvT200M_a5ss_jc)[1]))
names(AS)[names(AS) == 'rep("A5SS", dim(WTvT200M_a5ss_jc)[1])'] <- "events"
WTvT200M_a5ss_jc = cbind(WTvT200M_a5ss_jc,AS)
Comparison = as.data.frame(rep("WTvT200M",dim(WTvT200M_a5ss_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvT200M", dim(WTvT200M_a5ss_jc)[1])'] <- "Comparison"
WTvT200M_a5ss_jc = cbind(WTvT200M_a5ss_jc,Comparison)

WTvT200M_a5ss_jc = unite(WTvT200M_a5ss_jc,"Position",c(4:11),sep = ":",remove = T)
WTvT200M_a5ss_jc$EVENT <- paste(WTvT200M_a5ss_jc$geneSymbol,WTvT200M_a5ss_jc$Position,sep = "_")
rownames(WTvT200M_a5ss_jc) <- WTvT200M_a5ss_jc$EVENT
WTvT200M_a5ss_jc <- subset(WTvT200M_a5ss_jc, select = -c(1:5))

WTvT200M_a5ss_jc <- separate(WTvT200M_a5ss_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_a5ss_jc <- separate(WTvT200M_a5ss_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_a5ss_jc <- separate(WTvT200M_a5ss_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_T200M1","IJC_SAMPLE_T200M2","IJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_a5ss_jc <- separate(WTvT200M_a5ss_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_T200M1","SJC_SAMPLE_T200M2","SJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_a5ss_jc[1:12] <- as.numeric(unlist(WTvT200M_a5ss_jc[1:12]))

WTvT200M_a5ss_jc <- separate(WTvT200M_a5ss_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvT200M_a5ss_jc <- separate(WTvT200M_a5ss_jc, col = IncLevel2, into = c("IncLevel_T200M1","IncLevel_T200M2","IncLevel_T200M3"),sep = ",",remove = T)
WTvT200M_a5ss_jc[17:22] <- as.numeric(unlist(WTvT200M_a5ss_jc[17:22]))
WTvT200M_a5ss_jc <- na.omit(WTvT200M_a5ss_jc)
WTvT200M_a5ss_jc$PSIDiff <- (apply(WTvT200M_a5ss_jc[17:22], MARGIN =  1, f,))
WTvT200M_a5ss_jc$Coverage <- (apply(WTvT200M_a5ss_jc[c(1:3,7:9)], MARGIN = 1,mx,))
```



Filtering WT vs T200M A5SS JC by average reads, abs(IncLevelDifference), and FDR 
```{r}
WTvT200M_a5ss_jc = subset(WTvT200M_a5ss_jc,Coverage >=coverage)
WTvT200M_a5ss_jc <- subset(WTvT200M_a5ss_jc, abs(IncLevelDifference) >= IncLevelDifference.variable & FDR <= FDR.variable)
```



WT vs EV A5SS JC
```{r}
WTvEV_a5ss_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvEV/BAM/A5SS.MATS.JC.txt",header = T)
WTvEV_a5ss_jc <- as.data.frame(WTvEV_a5ss_jc)

AS = as.data.frame(rep("A5SS",dim(WTvEV_a5ss_jc)[1]))
names(AS)[names(AS) == 'rep("A5SS", dim(WTvEV_a5ss_jc)[1])'] <- "events"
WTvEV_a5ss_jc = cbind(WTvEV_a5ss_jc,AS)
Comparison = as.data.frame(rep("WTvEV",dim(WTvEV_a5ss_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvEV", dim(WTvEV_a5ss_jc)[1])'] <- "Comparison"
WTvEV_a5ss_jc = cbind(WTvEV_a5ss_jc,Comparison)

WTvEV_a5ss_jc = unite(WTvEV_a5ss_jc,"Position",c(4:11),sep = ":",remove = T)
WTvEV_a5ss_jc$EVENT <- paste(WTvEV_a5ss_jc$geneSymbol,WTvEV_a5ss_jc$Position,sep = "_")
rownames(WTvEV_a5ss_jc) <- WTvEV_a5ss_jc$EVENT
WTvEV_a5ss_jc <- subset(WTvEV_a5ss_jc, select = -c(1:5))

WTvEV_a5ss_jc <- separate(WTvEV_a5ss_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_a5ss_jc <- separate(WTvEV_a5ss_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_a5ss_jc <- separate(WTvEV_a5ss_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_EV1","IJC_SAMPLE_EV2","IJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_a5ss_jc <- separate(WTvEV_a5ss_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_EV1","SJC_SAMPLE_EV2","SJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_a5ss_jc[1:12] <- as.numeric(unlist(WTvEV_a5ss_jc[1:12]))

WTvEV_a5ss_jc <- separate(WTvEV_a5ss_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvEV_a5ss_jc <- separate(WTvEV_a5ss_jc, col = IncLevel2, into = c("IncLevel_EV1","IncLevel_EV2","IncLevel_EV3"),sep = ",",remove = T)
WTvEV_a5ss_jc[17:22] <- as.numeric(unlist(WTvEV_a5ss_jc[17:22]))
WTvEV_a5ss_jc <- na.omit(WTvEV_a5ss_jc)
WTvEV_a5ss_jc$PSIDiff <- (apply(WTvEV_a5ss_jc[17:22], MARGIN =  1, f,))
WTvEV_a5ss_jc$Coverage <- (apply(WTvEV_a5ss_jc[c(1:3,7:9)], MARGIN = 1,mx,))
```



Filtering WT vs EV A5SS JC by average reads, abs(IncLevelDifference), and FDR 
```{r}
WTvEV_a5ss_jc = subset(WTvEV_a5ss_jc,Coverage >=coverage)
WTvEV_a5ss_jc <- subset(WTvEV_a5ss_jc, abs(IncLevelDifference) >= IncLevelDifference.variable & FDR <= FDR.variable)
```



Combining A3SS (Only Events that have all three levels are included) this further filters the list
```{r}
A5SS <- merge(WTvT200M_a5ss_jc,WTvEV_a5ss_jc,by="EVENT",)
colnames(A5SS)<-gsub(".x","",colnames(A5SS))
A5SS <- subset(A5SS, select = c(1:13,35:40,18:23,48:50,25))
```



WT vs T200M MXE JC
```{r}
WTvT200M_mxe_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvT200M/BAM/MXE.MATS.JC.txt",header = T)
WTvT200M_mxe_jc <- as.data.frame(WTvT200M_mxe_jc)

AS = as.data.frame(rep("MXE",dim(WTvT200M_mxe_jc)[1]))
names(AS)[names(AS) == 'rep("MXE", dim(WTvT200M_mxe_jc)[1])'] <- "events"
WTvT200M_mxe_jc = cbind(WTvT200M_mxe_jc,AS)
Comparison = as.data.frame(rep("WTvT200M",dim(WTvT200M_mxe_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvT200M", dim(WTvT200M_mxe_jc)[1])'] <- "Comparison"
WTvT200M_mxe_jc = cbind(WTvT200M_mxe_jc,Comparison)

WTvT200M_mxe_jc = unite(WTvT200M_mxe_jc,"Position",c(4:13),sep = ":",remove = T)
WTvT200M_mxe_jc$EVENT <- paste(WTvT200M_mxe_jc$geneSymbol,WTvT200M_mxe_jc$Position,sep = "_")
rownames(WTvT200M_mxe_jc) <- WTvT200M_mxe_jc$EVENT
WTvT200M_mxe_jc <- subset(WTvT200M_mxe_jc, select = -c(1:5))

WTvT200M_mxe_jc <- separate(WTvT200M_mxe_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_mxe_jc <- separate(WTvT200M_mxe_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_mxe_jc <- separate(WTvT200M_mxe_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_T200M1","IJC_SAMPLE_T200M2","IJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_mxe_jc <- separate(WTvT200M_mxe_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_T200M1","SJC_SAMPLE_T200M2","SJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_mxe_jc[1:12] <- as.numeric(unlist(WTvT200M_mxe_jc[1:12]))

WTvT200M_mxe_jc <- separate(WTvT200M_mxe_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvT200M_mxe_jc <- separate(WTvT200M_mxe_jc, col = IncLevel2, into = c("IncLevel_T200M1","IncLevel_T200M2","IncLevel_T200M3"),sep = ",",remove = T)
WTvT200M_mxe_jc[17:22] <- as.numeric(unlist(WTvT200M_mxe_jc[17:22]))
WTvT200M_mxe_jc <- na.omit(WTvT200M_mxe_jc)
WTvT200M_mxe_jc$PSIDiff <- (apply(WTvT200M_mxe_jc[17:22], MARGIN =  1, f,))
WTvT200M_mxe_jc$Coverage <- (apply(WTvT200M_mxe_jc[c(1:3,7:9)], MARGIN = 1,mx,))
```



Filtering WT vs T200M MXE JC by average reads, abs(IncLevelDifference), and FDR 
```{r}
WTvT200M_mxe_jc = subset(WTvT200M_mxe_jc,Coverage >=coverage)
WTvT200M_mxe_jc <- subset(WTvT200M_mxe_jc, abs(IncLevelDifference) >= IncLevelDifference.variable & FDR <= FDR.variable)
```



WT vs EV MXE JC
```{r}
WTvEV_mxe_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvEV/BAM/MXE.MATS.JC.txt",header = T)
WTvEV_mxe_jc <- as.data.frame(WTvEV_mxe_jc)

AS = as.data.frame(rep("MXE",dim(WTvEV_mxe_jc)[1]))
names(AS)[names(AS) == 'rep("MXE", dim(WTvEV_mxe_jc)[1])'] <- "events"
WTvEV_mxe_jc = cbind(WTvEV_mxe_jc,AS)
Comparison = as.data.frame(rep("WTvEV",dim(WTvEV_mxe_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvEV", dim(WTvEV_mxe_jc)[1])'] <- "Comparison"
WTvEV_mxe_jc = cbind(WTvEV_mxe_jc,Comparison)

WTvEV_mxe_jc = unite(WTvEV_mxe_jc,"Position",c(4:13),sep = ":",remove = T)
WTvEV_mxe_jc$EVENT <- paste(WTvEV_mxe_jc$geneSymbol,WTvEV_mxe_jc$Position,sep = "_")
rownames(WTvEV_mxe_jc) <- WTvEV_mxe_jc$EVENT
WTvEV_mxe_jc <- subset(WTvEV_mxe_jc, select = -c(1:5))

WTvEV_mxe_jc <- separate(WTvEV_mxe_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_mxe_jc <- separate(WTvEV_mxe_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_mxe_jc <- separate(WTvEV_mxe_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_EV1","IJC_SAMPLE_EV2","IJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_mxe_jc <- separate(WTvEV_mxe_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_EV1","SJC_SAMPLE_EV2","SJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_mxe_jc[1:12] <- as.numeric(unlist(WTvEV_mxe_jc[1:12]))

WTvEV_mxe_jc <- separate(WTvEV_mxe_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvEV_mxe_jc <- separate(WTvEV_mxe_jc, col = IncLevel2, into = c("IncLevel_EV1","IncLevel_EV2","IncLevel_EV3"),sep = ",",remove = T)
WTvEV_mxe_jc[17:22] <- as.numeric(unlist(WTvEV_mxe_jc[17:22]))
WTvEV_mxe_jc <- na.omit(WTvEV_mxe_jc)
WTvEV_mxe_jc$PSIDiff <- (apply(WTvEV_mxe_jc[17:22], MARGIN =  1, f,))
WTvEV_mxe_jc$Coverage <- (apply(WTvEV_mxe_jc[c(1:3,7:9)], MARGIN = 1,mx,))
```



Filtering WT vs EV MXE JC by average reads, abs(IncLevelDifference), and FDR 
```{r}
WTvEV_mxe_jc = subset(WTvEV_mxe_jc,Coverage >=coverage)
WTvEV_mxe_jc <- subset(WTvEV_mxe_jc, abs(IncLevelDifference) >= IncLevelDifference.variable & FDR <= FDR.variable)
```



Combining MXE (Only Events that have all three levels are included) this further filters the list
```{r}
MXE <- merge(WTvT200M_mxe_jc,WTvEV_mxe_jc,by="EVENT",)
colnames(MXE)<-gsub(".x","",colnames(MXE))
MXE <- subset(MXE, select = c(1:13,35:40,18:23,48:50,25))
```



Combining ALL AS EVENTS that have been filtered
```{r}
Pengda_AS_events <- rbind(RI,SE,A3SS,A5SS,MXE)
Pengda_AS_events <- na.omit(Pengda_AS_events)
rownames(Pengda_AS_events) <- rownames(Pengda_AS_events$EVENT)
#write.csv(Pengda_AS_events,"Pengda-AS-JC-nonorm-50counts-INCLvl_FDR.csv")
```



PheatMap 
```{r}

Anno <- data.frame(EVENT = Pengda_AS_events$events)

rownames(Pengda_AS_events) <- Pengda_AS_events$EVENT
rownames(Anno) <- Pengda_AS_events$EVENT

pheatmap(Pengda_AS_events[20:28], cluster_rows=F, show_rownames=F,
         cluster_cols=F, main = "Filtered Events",border_color = F,
         annotation_row = Anno,scale = "row",
         color=colorRampPalette(c("red", "white", "blue"))(150),
         fontsize = 12)
```
```{r}

```







