---
title: "ASPengdaDataset-WTvsEV-JC"
author: "Kwame Forbes"
date: "10/3/2022"
output: html_document
---
load Dependencies
```{r}
#install.packages("tidyr")
library(tidyr)
#install.packages("plyr")
library("plyr")
install.packages("devtools")
library(devtools)
#devtools::install_github("kassambara/ggpubr")
#install.packages("ggpubr")
library(ggpubr)
#install.packages('scrime')
library("scrime")
library(pheatmap)
```

WT vs EV JC only.

Variables
```{r}
IncLevelDifference.variable = 0.1
FDR.variable = 0.05
coverage = 50
```


WT vs EV RI JC 
```{r}
WTvEV_ri_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvEV/BAM/RI.MATS.JC.txt",header = T)
WTvEV_ri_jc <- as.data.frame(WTvEV_ri_jc)

AS = as.data.frame(rep("RI",dim(WTvEV_ri_jc)[1]))
names(AS)[names(AS) == 'rep("RI", dim(WTvEV_ri_jc)[1])'] <- "events"
WTvEV_ri_jc = cbind(WTvEV_ri_jc,AS)
Comparison = as.data.frame(rep("WTvEV",dim(WTvEV_ri_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvEV", dim(WTvEV_ri_jc)[1])'] <- "Comparison"
WTvEV_ri_jc = cbind(WTvEV_ri_jc,Comparison)

WTvEV_ri_jc = unite(WTvEV_ri_jc,"Position",c(4:11),sep = ":",remove = T)
WTvEV_ri_jc$EVENT <- paste(WTvEV_ri_jc$geneSymbol,WTvEV_ri_jc$Position,sep = "_")
rownames(WTvEV_ri_jc) <- WTvEV_ri_jc$EVENT
WTvEV_ri_jc <- subset(WTvEV_ri_jc, select = -c(1:5))

WTvEV_ri_jc <- separate(WTvEV_ri_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_ri_jc <- separate(WTvEV_ri_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_ri_jc <- separate(WTvEV_ri_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_EV1","IJC_SAMPLE_EV2","IJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_ri_jc <- separate(WTvEV_ri_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_EV1","SJC_SAMPLE_EV2","SJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_ri_jc[1:12] <- as.numeric(unlist(WTvEV_ri_jc[1:12]))

WTvEV_ri_jc <- separate(WTvEV_ri_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvEV_ri_jc <- separate(WTvEV_ri_jc, col = IncLevel2, into = c("IncLevel_EV1","IncLevel_EV2","IncLevel_EV3"),sep = ",",remove = T)
WTvEV_ri_jc[17:22] <- as.numeric(unlist(WTvEV_ri_jc[17:22]))
WTvEV_ri_jc <- na.omit(WTvEV_ri_jc)
```
Filtering WT vs EV RI JC average reads, abs(IncLevelDifference), and FDR 
```{r}
WTvEV_ri_jc <- subset(WTvEV_ri_jc,
                         apply(WTvEV_ri_jc[c(1,4)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_ri_jc[c(2,5)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_ri_jc[c(3,6)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_ri_jc[c(7,10)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_ri_jc[c(8,11)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_ri_jc[c(9,12)], MARGIN =  1,mean)>=coverage)

WTvEV_ri_jc <- subset(WTvEV_ri_jc, abs(IncLevelDifference) >= IncLevelDifference.variable & FDR <= FDR.variable)
```



WT vs EV SE JC
```{r}
WTvEV_se_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvEV/BAM/SE.MATS.JC.txt",header = T)
WTvEV_se_jc <- as.data.frame(WTvEV_se_jc)

AS = as.data.frame(rep("SE",dim(WTvEV_se_jc)[1]))
names(AS)[names(AS) == 'rep("SE", dim(WTvEV_se_jc)[1])'] <- "events"
WTvEV_se_jc = cbind(WTvEV_se_jc,AS)
Comparison = as.data.frame(rep("WTvEV",dim(WTvEV_se_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvEV", dim(WTvEV_se_jc)[1])'] <- "Comparison"
WTvEV_se_jc = cbind(WTvEV_se_jc,Comparison)

WTvEV_se_jc = unite(WTvEV_se_jc,"Position",c(4:11),sep = ":",remove = T)
WTvEV_se_jc$EVENT <- paste(WTvEV_se_jc$geneSymbol,WTvEV_se_jc$Position,sep = "_")
rownames(WTvEV_se_jc) <- WTvEV_se_jc$EVENT
WTvEV_se_jc <- subset(WTvEV_se_jc, select = -c(1:5))

WTvEV_se_jc <- separate(WTvEV_se_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_se_jc <- separate(WTvEV_se_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_se_jc <- separate(WTvEV_se_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_EV1","IJC_SAMPLE_EV2","IJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_se_jc <- separate(WTvEV_se_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_EV1","SJC_SAMPLE_EV2","SJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_se_jc[1:12] <- as.numeric(unlist(WTvEV_se_jc[1:12]))

WTvEV_se_jc <- separate(WTvEV_se_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvEV_se_jc <- separate(WTvEV_se_jc, col = IncLevel2, into = c("IncLevel_EV1","IncLevel_EV2","IncLevel_EV3"),sep = ",",remove = T)
WTvEV_se_jc[17:22] <- as.numeric(unlist(WTvEV_se_jc[17:22]))
WTvEV_se_jc <- na.omit(WTvEV_se_jc)
```



Filtering WT vs EV SE JC by average reads, abs(IncLevelDifference), and FDR 
```{r}
WTvEV_se_jc <- subset(WTvEV_se_jc,
                         apply(WTvEV_se_jc[c(1,4)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_se_jc[c(2,5)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_se_jc[c(3,6)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_se_jc[c(7,10)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_se_jc[c(8,11)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_se_jc[c(9,12)], MARGIN =  1,mean)>=coverage)

WTvEV_se_jc <- subset(WTvEV_se_jc, abs(IncLevelDifference) >= IncLevelDifference.variable & FDR <= FDR.variable)
```




WT vs EV A3SS JC
```{r}
WTvEV_a3ss_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvEV/BAM/A3SS.MATS.JC.txt",header = T)
WTvEV_a3ss_jc <- as.data.frame(WTvEV_a3ss_jc)

AS = as.data.frame(rep("A3SS",dim(WTvEV_a3ss_jc)[1]))
names(AS)[names(AS) == 'rep("A3SS", dim(WTvEV_a3ss_jc)[1])'] <- "events"
WTvEV_a3ss_jc = cbind(WTvEV_a3ss_jc,AS)
Comparison = as.data.frame(rep("WTvEV",dim(WTvEV_a3ss_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvEV", dim(WTvEV_a3ss_jc)[1])'] <- "Comparison"
WTvEV_a3ss_jc = cbind(WTvEV_a3ss_jc,Comparison)

WTvEV_a3ss_jc = unite(WTvEV_a3ss_jc,"Position",c(4:11),sep = ":",remove = T)
WTvEV_a3ss_jc$EVENT <- paste(WTvEV_a3ss_jc$geneSymbol,WTvEV_a3ss_jc$Position,sep = "_")
rownames(WTvEV_a3ss_jc) <- WTvEV_a3ss_jc$EVENT
WTvEV_a3ss_jc <- subset(WTvEV_a3ss_jc, select = -c(1:5))

WTvEV_a3ss_jc <- separate(WTvEV_a3ss_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_a3ss_jc <- separate(WTvEV_a3ss_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_a3ss_jc <- separate(WTvEV_a3ss_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_EV1","IJC_SAMPLE_EV2","IJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_a3ss_jc <- separate(WTvEV_a3ss_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_EV1","SJC_SAMPLE_EV2","SJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_a3ss_jc[1:12] <- as.numeric(unlist(WTvEV_a3ss_jc[1:12]))

WTvEV_a3ss_jc <- separate(WTvEV_a3ss_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvEV_a3ss_jc <- separate(WTvEV_a3ss_jc, col = IncLevel2, into = c("IncLevel_EV1","IncLevel_EV2","IncLevel_EV3"),sep = ",",remove = T)
WTvEV_a3ss_jc[17:22] <- as.numeric(unlist(WTvEV_a3ss_jc[17:22]))
WTvEV_a3ss_jc <- na.omit(WTvEV_a3ss_jc)
```



Filtering WT vs EV A3SS JC by average reads, abs(IncLevelDifference), and FDR 
```{r}
WTvEV_a3ss_jc <- subset(WTvEV_a3ss_jc,
                         apply(WTvEV_a3ss_jc[c(1,4)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_a3ss_jc[c(2,5)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_a3ss_jc[c(3,6)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_a3ss_jc[c(7,10)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_a3ss_jc[c(8,11)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_a3ss_jc[c(9,12)], MARGIN =  1,mean)>=coverage)

WTvEV_a3ss_jc <- subset(WTvEV_a3ss_jc, abs(IncLevelDifference) >= IncLevelDifference.variable & FDR <= FDR.variable)
```





WT vs EV A5SS JC
```{r}
WTvEV_a5ss_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvEV/BAM/A5SS.MATS.JC.txt",header = T)
WTvEV_a5ss_jc <- as.data.frame(WTvEV_a5ss_jc)

AS = as.data.frame(rep("A5SS",dim(WTvEV_a5ss_jc)[1]))
names(AS)[names(AS) == 'rep("A5SS", dim(WTvEV_a5ss_jc)[1])'] <- "events"
WTvEV_a5ss_jc = cbind(WTvEV_a5ss_jc,AS)
Comparison = as.data.frame(rep("WTvEV",dim(WTvEV_a5ss_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvEV", dim(WTvEV_a5ss_jc)[1])'] <- "Comparison"
WTvEV_a5ss_jc = cbind(WTvEV_a5ss_jc,Comparison)

WTvEV_a5ss_jc = unite(WTvEV_a5ss_jc,"Position",c(4:11),sep = ":",remove = T)
WTvEV_a5ss_jc$EVENT <- paste(WTvEV_a5ss_jc$geneSymbol,WTvEV_a5ss_jc$Position,sep = "_")
rownames(WTvEV_a5ss_jc) <- WTvEV_a5ss_jc$EVENT
WTvEV_a5ss_jc <- subset(WTvEV_a5ss_jc, select = -c(1:5))

WTvEV_a5ss_jc <- separate(WTvEV_a5ss_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_a5ss_jc <- separate(WTvEV_a5ss_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_a5ss_jc <- separate(WTvEV_a5ss_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_EV1","IJC_SAMPLE_EV2","IJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_a5ss_jc <- separate(WTvEV_a5ss_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_EV1","SJC_SAMPLE_EV2","SJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_a5ss_jc[1:12] <- as.numeric(unlist(WTvEV_a5ss_jc[1:12]))

WTvEV_a5ss_jc <- separate(WTvEV_a5ss_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvEV_a5ss_jc <- separate(WTvEV_a5ss_jc, col = IncLevel2, into = c("IncLevel_EV1","IncLevel_EV2","IncLevel_EV3"),sep = ",",remove = T)
WTvEV_a5ss_jc[17:22] <- as.numeric(unlist(WTvEV_a5ss_jc[17:22]))
WTvEV_a5ss_jc <- na.omit(WTvEV_a5ss_jc)
```



Filtering WT vs EV A5SS JC by average reads, abs(IncLevelDifference), and FDR 
```{r}
WTvEV_a5ss_jc <- subset(WTvEV_a5ss_jc,
                         apply(WTvEV_a5ss_jc[c(1,4)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_a5ss_jc[c(2,5)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_a5ss_jc[c(3,6)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_a5ss_jc[c(7,10)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_a5ss_jc[c(8,11)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_a5ss_jc[c(9,12)], MARGIN =  1,mean)>=coverage)

WTvEV_a5ss_jc <- subset(WTvEV_a5ss_jc, abs(IncLevelDifference) >= IncLevelDifference.variable & FDR <= FDR.variable)
```




WT vs EV MXE JC
```{r}
WTvEV_mxe_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvEV/BAM/MXE.MATS.JC.txt",header = T)
WTvEV_mxe_jc <- as.data.frame(WTvEV_mxe_jc)

AS = as.data.frame(rep("MXE",dim(WTvEV_mxe_jc)[1]))
names(AS)[names(AS) == 'rep("MXE", dim(WTvEV_mxe_jc)[1])'] <- "events"
WTvEV_mxe_jc = cbind(WTvEV_mxe_jc,AS)
Comparison = as.data.frame(rep("WTvEV",dim(WTvEV_mxe_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvEV", dim(WTvEV_mxe_jc)[1])'] <- "Comparison"
WTvEV_mxe_jc = cbind(WTvEV_mxe_jc,Comparison)

WTvEV_mxe_jc = unite(WTvEV_mxe_jc,"Position",c(4:13),sep = ":",remove = T)
WTvEV_mxe_jc$EVENT <- paste(WTvEV_mxe_jc$geneSymbol,WTvEV_mxe_jc$Position,sep = "_")
rownames(WTvEV_mxe_jc) <- WTvEV_mxe_jc$EVENT
WTvEV_mxe_jc <- subset(WTvEV_mxe_jc, select = -c(1:5))

WTvEV_mxe_jc <- separate(WTvEV_mxe_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_mxe_jc <- separate(WTvEV_mxe_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvEV_mxe_jc <- separate(WTvEV_mxe_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_EV1","IJC_SAMPLE_EV2","IJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_mxe_jc <- separate(WTvEV_mxe_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_EV1","SJC_SAMPLE_EV2","SJC_SAMPLE_EV3"),sep = ",",remove = T)
WTvEV_mxe_jc[1:12] <- as.numeric(unlist(WTvEV_mxe_jc[1:12]))

WTvEV_mxe_jc <- separate(WTvEV_mxe_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvEV_mxe_jc <- separate(WTvEV_mxe_jc, col = IncLevel2, into = c("IncLevel_EV1","IncLevel_EV2","IncLevel_EV3"),sep = ",",remove = T)
WTvEV_mxe_jc[17:22] <- as.numeric(unlist(WTvEV_mxe_jc[17:22]))
WTvEV_mxe_jc <- na.omit(WTvEV_mxe_jc)
```



Filtering WT vs EV MXE JC by average reads, abs(IncLevelDifference), and FDR 
```{r}
WTvEV_mxe_jc <- subset(WTvEV_mxe_jc,
                         apply(WTvEV_mxe_jc[c(1,4)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_mxe_jc[c(2,5)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_mxe_jc[c(3,6)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_mxe_jc[c(7,10)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_mxe_jc[c(8,11)], MARGIN =  1,mean)>=coverage
                         &apply(WTvEV_mxe_jc[c(9,12)], MARGIN =  1,mean)>=coverage)

WTvEV_mxe_jc <- subset(WTvEV_mxe_jc, abs(IncLevelDifference) >= IncLevelDifference.variable & FDR <= FDR.variable)
```





Combining ALL AS EVENTS that have been filtered
```{r}
WTvEV_jc <- rbind(WTvEV_ri_jc,WTvEV_se_jc,WTvEV_a3ss_jc,WTvEV_a5ss_jc,WTvEV_mxe_jc)
rownames(WTvEV_jc) <- rownames(WTvEV_jc$EVENT)
colnames(WTvEV_jc)<-gsub("IncLevel_","PSI_",colnames(WTvEV_jc))
```



PheatMap 
```{r}

Anno <- data.frame(EVENT = WTvEV_jc$events)

rownames(WTvEV_jc) <- WTvEV_jc$EVENT
rownames(Anno) <- WTvEV_jc$EVENT

pheatmap(WTvEV_jc[17:22], cluster_rows=F, show_rownames=F,
         cluster_cols=F, main = "Filtered Events",border_color = F,
         annotation_row = Anno,scale = "row",
         color=colorRampPalette(c("red", "white", "blue"))(200),
         fontsize = 12)
```
```{r}

```


Plots
```{r}
p <- ggplot(data = WTvEV_ri_jc,mapping= 
              aes(IncLevelDifference,-log(FDR)))+ theme_classic() + geom_point(color = ifelse(WTvEV_ri_jc$IncLevelDifference >= 0.1 ,"blue","red")) + 
  theme_classic()+ ggtitle("WT vs. EV RI PSI") +xlab("PSI Change") + ylab("-log10(FDR)")
pp <- p+ theme(plot.title = element_text(color="red", size=14, face="bold.italic"),
         axis.title.x = element_text(color="blue", size=14, face="bold"),
         axis.title.y = element_text(color="#993333", size=14, face="bold"))

s <- ggplot(WTvEV_ri_jc, aes(x="WTvEV", y=IncLevelDifference)) + 
   theme_classic()+ ggtitle("RI PSI of WTvEV") + ylab("IncLevelDifference") + geom_violin()

s2 <- s + theme(plot.title = element_text(color="red", size=14, face="bold.italic"),
         axis.title.x = element_text(color="blue", size=14, face="bold"),
         axis.title.y = element_text(color="#993333", size=14, face="bold"))
 
s2 <- s2 + geom_boxplot(width=0.2)

sg <- ggarrange(pp,s2, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
sg
```





